---
title: "XX"
author : "Jishnu Veerapaneni"
format: html

execute: 
    echo: false
---


```{r}
#| message: false
library(tidyverse)
library(primer.data)
library(tidymodels)
library(broom)
library(easystats)
```

We are examining Georgia voters attitudes towards immigration. The data source being used is past survey results about immigration from a year ago or more and we attempt to examine how exposure to Spanish-speakers effects voter attitudes toward immigration? A potential weakness in our model is that we are examining voter attitudes toward immigration in Georgia today, but we are using data from a 2012 experiment with Boston commuters, but when in reality there are non-commuters in Georgia and the time period difference might have cause a difference in political ideologies for the state and people. We modeled attitudes toward immigration, measured as a continuous score reflecting the favorability toward immigration policies, as a linear function of exposure to Spanish speakers. The model estimates the causal effect of this exposure on immigration attitudes among registered voters in Georgia, based on data adapted from a 2012 experiment among Boston commuters.

$$Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \cdots + \beta_n X_n + \epsilon$$

with $\epsilon \sim \mathcal{N}(0, \sigma^2)$.





```{r}
linear_reg(engine = "lm") |>
fit(att_end ~ treatment, data = trains)|>
tidy(conf.int = TRUE)
fit_att <- linear_reg(engine = "lm") |> 
  fit(att_end ~ treatment, data = trains)
```



```{r}
#| cache: true



```

$$\widehat{\text{att_end}} = 8.45 + 1.55 \cdot \text{treatment}_{\text{Treated}}$$




```{r}
#| label: tbl-fit-results
#| tbl-cap: "Regression Results with Estimates and Confidence Intervals"

library(kableExtra)
library(tidyverse)

# Assuming fit_att is the fitted model and tidy() is called with confidence intervals
results <- tidy(fit_att, conf.int = TRUE) %>%
  select(term, estimate, conf.low, conf.high) %>%
  mutate(
    estimate = round(estimate, 2),
    conf.low = round(conf.low, 2),
    conf.high = round(conf.high, 2),
    ci = paste0("[", conf.low, ", ", conf.high, "]")
  ) %>%
  select(term, estimate, ci)

# Create a formatted table
results %>%
  kable(
    col.names = c("Term", "Estimate", "95% CI"),
    align = c("l", "c", "c"),
    digits = 2
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = FALSE
  )
```

